Why aren't significance tests commonly used for linear regression diagnostics?

### 2022-11-22 paper_comparison/paper_comparison/paper_comparison.Rmd
clean up plots in the result

```{r power-poly-uniform, fig.cap = "..."}
vi_survey %>%
  filter(x_dist == "uniform") %>%
  group_by(unique_lineup_id) %>%
  summarise(across(everything(), first)) %>%
  filter(type == "polynomial") %>%
  filter(!null_lineup) %>%
  filter(!attention_check) %>%
  mutate(reject_dirichlet = as.numeric(p_value <= 0.05)) %>%
  mutate(log_effect_size = log(effect_size)) %>%
  ggplot() +
  geom_smooth(aes(log_effect_size, reject_dirichlet, col = "Visual test"), method = "glm", method.args = list(family = binomial), se = FALSE) +
  stat_smooth(geom = "line", 
              data = ~boot_y(.x, reject_dirichlet, times = 500), 
              aes(log_effect_size, reject_dirichlet, group = boot_id, col = "Visual test"), 
              method = "glm", 
              method.args = list(family = binomial), 
              se = FALSE, 
              alpha = 0.03) +
  geom_smooth(data = mutate(poly_conv_sim, log_effect_size = log(effect_size)) %>%
                filter(x_dist == "uniform") %>%
                pivot_longer(F_p_value:SW_p_value) %>%
                mutate(name = gsub("_p_value", " test", name)), 
              aes(log_effect_size, as.numeric(value < 0.05), col = name), 
              method = "glm", 
              method.args = list(family = binomial),
              se = FALSE) +
  geom_point(aes(log_effect_size, prop_detect), alpha = 0.3) + geom_point(data = ~filter(.x, unique_lineup_id %in% c("poly_166", "poly_269", "poly_396", "poly_574")), aes(log_effect_size, prop_detect), alpha = 1, col = "red", size = 2) +
  theme_light(base_size = 5) +
  scale_color_brewer(palette = "Dark2", direction = -1) +
  xlab("Natural logarithm of effect size") +
  ylab("Power") -> p

@@

```{r, fig.cap="..."}
vi_survey %>%
  mutate(x_dist = ifelse(x_dist == "even_discrete", "discrete uniform", x_dist)) %>%
  group_by(unique_lineup_id) %>%
  summarise(across(everything(), first)) %>%
  filter(!null_lineup) %>%
  filter(!attention_check) %>%
  mutate(reject_dirichlet = as.numeric(p_value <= 0.05)) %>%
  mutate(log_effect_size = log(effect_size)) %>%
  ggplot() +
  geom_smooth(aes(log_effect_size, reject_dirichlet, col = "Visual test"), method = "glm", method.args = list(family = binomial), se = FALSE) +
  geom_smooth(data = mutate(poly_conv_sim, log_effect_size = log(effect_size)) %>%
                pivot_longer(F_p_value:SW_p_value) %>%
                mutate(name = gsub("_p_value", " test", name)) %>%
                mutate(type = "polynomial") %>%
                mutate(x_dist = ifelse(x_dist == "even_discrete", "discrete uniform", x_dist)) %>%
                bind_rows(mutate(heter_conv_sim, log_effect_size = log(effect_size)) %>%
                pivot_longer(F_p_value:SW_p_value) %>%
                mutate(name = gsub("_p_value", " test", name)) %>%
                mutate(type = "heteroskedasticity") %>%
                mutate(x_dist = ifelse(x_dist == "even_discrete", "discrete uniform", x_dist))), 
              aes(log_effect_size, as.numeric(value < 0.05), col = name), 
              method = "glm", 
              method.args = list(family = binomial),
              se = FALSE) +
  theme_light(base_size = 5) +
  scale_color_brewer(palette = "Dark2", direction = -1) +
  xlab("Natural logarithm of effect size") +
  ylab("Power") +
  facet_grid(x_dist~type)
```

```{r}
vi_survey %>%
  mutate(x_dist = ifelse(x_dist == "even_discrete", "discrete uniform", x_dist)) %>%
  group_by(unique_lineup_id) %>%
  summarise(across(everything(), first)) %>%
  filter(!null_lineup) %>%
  filter(!attention_check) %>%
  mutate(reject_dirichlet = as.numeric(p_value <= 0.05)) %>%
  mutate(log_effect_size = log(effect_size)) %>%
  ggplot() +
  geom_smooth(aes(log_effect_size, reject_dirichlet, col = "Visual test"), method = "glm", method.args = list(family = binomial), se = FALSE) +
  geom_smooth(data = mutate(poly_conv_sim, log_effect_size = log(effect_size)) %>%
                pivot_longer(F_p_value:SW_p_value) %>%
                mutate(name = gsub("_p_value", " test", name)) %>%
                mutate(type = "polynomial") %>%
                mutate(x_dist = ifelse(x_dist == "even_discrete", "discrete uniform", x_dist)) %>%
                bind_rows(mutate(heter_conv_sim, log_effect_size = log(effect_size)) %>%
                pivot_longer(F_p_value:SW_p_value) %>%
                mutate(name = gsub("_p_value", " test", name)) %>%
                mutate(type = "heteroskedasticity") %>%
                mutate(x_dist = ifelse(x_dist == "even_discrete", "discrete uniform", x_dist))), 
              aes(log_effect_size, as.numeric(value < 0.05), col = name), 
              method = "glm", 
              method.args = list(family = binomial),
              se = FALSE) +
  theme_light(base_size = 5) +
  scale_color_brewer(palette = "Dark2", direction = -1) +
  xlab("Natural logarithm of effect size") +
  ylab("Power") +
  facet_grid(shape~type)
```

>>>>

```{r power-poly-uniform, fig.cap = "...", eval = FALSE}
vi_survey %>%
  filter(x_dist == "uniform") %>%
  group_by(unique_lineup_id) %>%
  summarise(across(everything(), first)) %>%
  filter(type == "polynomial") %>%
  filter(!null_lineup) %>%
  filter(!attention_check) %>%
  mutate(reject_dirichlet = as.numeric(p_value <= 0.05)) %>%
  mutate(log_effect_size = log(effect_size)) %>%
  ggplot() +
  geom_smooth(aes(log_effect_size, reject_dirichlet, col = "Visual test"), method = "glm", method.args = list(family = binomial), se = FALSE) +
  stat_smooth(geom = "line", 
              data = ~boot_y(.x, reject_dirichlet, times = 500), 
              aes(log_effect_size, reject_dirichlet, group = boot_id, col = "Visual test"), 
              method = "glm", 
              method.args = list(family = binomial), 
              se = FALSE, 
              alpha = 0.03) +
  geom_smooth(data = mutate(poly_conv_sim, log_effect_size = log(effect_size)) %>%
                filter(x_dist == "uniform") %>%
                pivot_longer(F_p_value:SW_p_value) %>%
                mutate(name = gsub("_p_value", " test", name)), 
              aes(log_effect_size, as.numeric(value < 0.05), col = name), 
              method = "glm", 
              method.args = list(family = binomial),
              se = FALSE) +
  geom_point(aes(log_effect_size, prop_detect), alpha = 0.3) + geom_point(data = ~filter(.x, unique_lineup_id %in% c("poly_166", "poly_269", "poly_396", "poly_574")), aes(log_effect_size, prop_detect), alpha = 1, col = "red", size = 2) +
  theme_light(base_size = 5) +
  scale_color_brewer(palette = "Dark2", direction = -1) +
  xlab("Natural logarithm of effect size") +
  ylab("Power") -> p

@@

### 2022-11-22 paper_comparison/paper_comparison/paper_comparison.tex
clean up plots in the result

{\centering \includegraphics[width=1\linewidth]{paper_comparison_files/figure-latex/power-poly-uniform-1}

\caption{...}\label{fig:power-poly-uniform}
\end{figure}

@@

{\centering \includegraphics[width=1\linewidth]{paper_comparison_files/figure-latex/unnamed-chunk-8-1}

\caption{...}\label{fig:unnamed-chunk-8}
\end{figure}

\begin{center}\includegraphics[width=1\linewidth]{paper_comparison_files/figure-latex/unnamed-chunk-9-1} \end{center}

>>>>

\begin{center}\includegraphics[width=1\linewidth]{paper_comparison_files/figure-latex/unnamed-chunk-7-1} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{paper_comparison_files/figure-latex/unnamed-chunk-7-2} \end{center}

@@
